\vspace{-15mm} \fontsize{24pt}{10pt}\selectfont \textbf{Traversing Symmetric NAT with predictable port allocation function}

### 2013-12-07 paper.tex
expected value

Moreover we assume incremental NAT with $\Delta=1$ on both sides. If we sample the NAT 
state\footnote{One new STUN request to determine current port number. Creates new NAT allocation.}
each $T=10$~milliseconds the NAT state can be modeled as a random process $\{C_i | C_i \in \mathbb{N}, C_i \geq i, i\geq0\}$ where:
\[
C_i = \begin{dcases*}
         0 & if $i=0$ \\
         C_{i-1} + 1 + X_i, \; X_i \sim Po(\lambda T) & otherwise 
        \end{dcases*}
\]

@@

\begin{mydef}
Expected port value algorithm
\[
u \in \mathcal{U}, s \in \mathcal{S}, \lambda \in \mathcal{M}:\;
\mathcal{A}(u, s, \lambda) = (0, s(1 + \lambda T))
\]
\end{mydef}

ToDo: give an argument that algorithm in each step computes expected value on port number in given time...

@@

>>>>

Moreover we assume incremental NAT with $\Delta=1$ on both sides. If we sample the NAT 
state\footnote{One new STUN request to determine current port number. Creates new NAT allocation.}
each $T=10$~milliseconds the NAT state can be modeled as a random process $\{C_i | C_i \in \mathbb{N}, C_i \geq i, i\geq0\}$ where:
\[
C_i = \begin{dcases*}
         0 & if $i=0$ \\
         C_{i-1} + 1 + X_i, \; X_i \sim Po(\lambda T) & otherwise 
        \end{dcases*}
\]
Rewritten as $C_i = i + \sum_{j=1}^{i}X_i$. Expected value $E[C_i] = i + E[\sum_{j=1}^{i}X_i] = i (1+\lambda T)$.

@@

\begin{mydef}
Expected port value algorithm
\begin{align*}
& u \in \mathcal{U}, s \in \mathcal{S}, \lambda \in \mathcal{M}:\\
& \mathcal{A}(u, s, \lambda) = (0, s(1 + \lambda T))
\end{align*}
\end{mydef}

In step $i$ algorithm tries the expected value for $C_i$. Since the $C_i$ has unimodal distribution
the expected value is also most probable value and the algorithm uses maximum likelihood approach.

@@

Success rate of the algorithm strongly relies on accurate measurements of the network 
properties the client resides in.  Usually
